### 2022-10-15 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@2d3c915013683172c3822b260d54b299712a9a5e 🚀

\vfill
Ecosystems are composed of networks of interacting species. These
interactions allow communities of species to persist through time
through both neutral and adaptive processes. Still a robust
understanding of, and ability to predict and forecast interactions among
species and their consequences for network structure remains elusive.
This knowledge-gap is largely driven by a shortfall of data---although
species occurrence data has rapidly increased in the last decade,
species interaction data has not kept pace, largely due to the intrinsic
difficulty and effort required to sample interactions. These sampling
challenges bias data and hinder inferences about the structure and
dynamics of interactions networks. Here, we demonstrate the realized
false-negative rate (the percentage of species that actually interact
but for which we do not yet have a record) can be quite high, even in
thoroughly sampled systems, due to the intrinsic variation in abundances
across species in a community. We demonstrate how a null model of
occurrence detection can be used to estimate the false-negative rate in
a given dataset. One hypothesis is that interactions between ``rare''
species are themselves rare because these species are less likely to
encounter one-another than species of higher relative abundance.
However, we demonstrate that across several datasets of spatial or
temporally replicated networks, there are positive associations that
suggest these interactions actually exist but just are not observed.
Finally, we assess how false negatives influence various models of
network prediction, and recommend directly accounting for observation
error in predictive models. We conclude by discussing how the
understanding of false-negatives can inform how we design monitoring
schemes for species interactions.

>>>>

        {\bfseries Abstract:}\,Ecosystems are composed of networks of
interacting species. These interactions allow communities of species to
persist through time through both neutral and adaptive processes. Still
a robust understanding of, and ability to predict and forecast
interactions among species and their consequences for network structure
remains elusive. This knowledge-gap is largely driven by a shortfall of
data---although species occurrence data has rapidly increased in the
last decade, species interaction data has not kept pace, largely due to
the intrinsic difficulty and effort required to sample interactions.
These sampling challenges bias data and hinder inferences about the
structure and dynamics of interactions networks. Here, we demonstrate
the realized false-negative rate (the percentage of species that
actually interact but for which we do not yet have a record) can be
quite high, even in thoroughly sampled systems, due to the intrinsic
variation in abundances across species in a community. We demonstrate
how a null model of occurrence detection can be used to estimate the
false-negative rate in a given dataset. One hypothesis is that
interactions between ``rare'' species are themselves rare because these
species are less likely to encounter one-another than species of higher
relative abundance. However, we demonstrate that across several datasets
of spatial or temporally replicated networks, there are positive
associations that suggest these interactions actually exist but just are
not observed. Finally, we assess how false negatives influence various
models of network prediction, and recommend directly accounting for
observation error in predictive models. We conclude by discussing how
the understanding of false-negatives can inform how we design monitoring
schemes for species interactions.\\%

### 2022-10-15 preprint.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@e4fd466051dbfde60cffbb8cd04dde4c658868d8 🚀
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@2d3c915013683172c3822b260d54b299712a9a5e 🚀

\usepackage{tikz}
\begin{document}
\tikz [remember picture, overlay] %
\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.4] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
\pagestyle{normal}
\thispagestyle{firstpage}

@@

Ecosystems are composed of networks of interacting species. These
interactions allow communities of species to persist through time
through both neutral and adaptive processes. Still a robust
understanding of, and ability to predict and forecast interactions among
species and their consequences for network structure remains elusive.
This knowledge-gap is largely driven by a shortfall of data---although
species occurrence data has rapidly increased in the last decade,
species interaction data has not kept pace, largely due to the intrinsic
difficulty and effort required to sample interactions. These sampling
challenges bias data and hinder inferences about the structure and
dynamics of interactions networks. Here, we demonstrate the realized
false-negative rate (the percentage of species that actually interact
but for which we do not yet have a record) can be quite high, even in
thoroughly sampled systems, due to the intrinsic variation in abundances
across species in a community. We demonstrate how a null model of
occurrence detection can be used to estimate the false-negative rate in
a given dataset. One hypothesis is that interactions between ``rare''
species are themselves rare because these species are less likely to
encounter one-another than species of higher relative abundance.
However, we demonstrate that across several datasets of spatial or
temporally replicated networks, there are positive associations that
suggest these interactions actually exist but just are not observed.
Finally, we assess how false negatives influence various models of
network prediction, and recommend directly accounting for observation
error in predictive models. We conclude by discussing how the
understanding of false-negatives can inform how we design monitoring
schemes for species interactions.

>>>>

\usepackage{tikz}
\begin{document}
\tikz [remember picture, overlay] %
\node [shift={(-0.6in,1.1cm)},scale=0.2,opacity=0.9] at (current page.south east)[anchor=south east]{\includegraphics{logo}};%
\pagestyle{normal}
\thispagestyle{firstpage}

@@

        {\bfseries Abstract:}\,Ecosystems are composed of networks of
interacting species. These interactions allow communities of species to
persist through time through both neutral and adaptive processes. Still
a robust understanding of, and ability to predict and forecast
interactions among species and their consequences for network structure
remains elusive. This knowledge-gap is largely driven by a shortfall of
data---although species occurrence data has rapidly increased in the
last decade, species interaction data has not kept pace, largely due to
the intrinsic difficulty and effort required to sample interactions.
These sampling challenges bias data and hinder inferences about the
structure and dynamics of interactions networks. Here, we demonstrate
the realized false-negative rate (the percentage of species that
actually interact but for which we do not yet have a record) can be
quite high, even in thoroughly sampled systems, due to the intrinsic
variation in abundances across species in a community. We demonstrate
how a null model of occurrence detection can be used to estimate the
false-negative rate in a given dataset. One hypothesis is that
interactions between ``rare'' species are themselves rare because these
species are less likely to encounter one-another than species of higher
relative abundance. However, we demonstrate that across several datasets
of spatial or temporally replicated networks, there are positive
associations that suggest these interactions actually exist but just are
not observed. Finally, we assess how false negatives influence various
models of network prediction, and recommend directly accounting for
observation error in predictive models. We conclude by discussing how
the understanding of false-negatives can inform how we design monitoring
schemes for species interactions.\\%
